---
title: "Two years of R-Ladies Melbourne"
author: "R-Ladies melbourne"
date: "Two years anniversary!"
output:
  html_document:
    theme: cosmo
    toc: yes
    includes:
      after_body:
      - header.html
      - footer.html
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(magick)
library(png)
library(grid)
library(emo)
library(icon)
```

Time flies and it's already two years after our lounch event. And like when you finish a holiday and you start remembering all the best moments (can't really think of any bad one!), I decided to spend some time to collect the pieces of a special year for the Aussie R and R-Ladies community. 

We celebrated our first anniversary a little bit more than a year ago, where we got to about 600 members on Meetup and in 2018 we celebrated again on the 17th of October having reached more than 1000 members!
As before, we held an event every month from February to December. We couldn't really be happier to see the large participation to our events across the year. Of course, we are not going to claim that we usually had 500 members participating at our event (we would really need to hire a bigger place...) but the fact that the number of members as well as the number that we see at every event keeps a steady increase, tells us that this group like this is still needed and is still attracting more interest! 


```{r fig.cap="New members on meetup and events from October 2017 to October 2018.", echo = FALSE,fig.asp=0.50}
img <- readPNG("AllPhotos/time_series.png")
grid.raster(img)
```

<br>

```{r fig.cap="Speakers from November 2017 to October 2018", echo = FALSE,fig.asp=0.50}
img <- readPNG("AllPhotos/faces2018.png")
grid.raster(img)
```


<br>

# A year of FIRST time things

2018 was the year of a few **FIRST** things that happened for our group. It was the first time that we:

* Participated to the useR! conference and granted scholarships to participants.
* Organised a mini conference with lightning talks and a panel discussion to celebrate our two years anniversary.
* Organised a lunch meetup, which hopefully is the first one of many to come!
* Decided, studied and planned to become a not-for-profit organisations (it will happen February 2019!)

To go in order, I would like to tell you a bit about the above. 

# useR! 2018

## Getting all together!

useR! 2018 was such an amazing experience for me personally and I believe for the all R Australian community as well. I found myself in the most ideal place and it was a refreshing five days immersion with people that love and work for same thing and most of whom I had just seen on Twitter by then and never met in person. How cool was that we could chat at the same table with R-Ladies from variaous parts of Australia and the whole world? We had the opportunity to discuss among each other about our experience in organising events, how everyone goes about looking for sponsors, or give suggestion about looking for speakers.

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Here are amazing <a href="https://twitter.com/hashtag/RLadies?src=hash&amp;ref_src=twsrc%5Etfw">#RLadies</a> from around the world having dinner after an excellent day at <a href="https://twitter.com/useR2018_conf?ref_src=twsrc%5Etfw">@useR2018_conf</a> <a href="https://twitter.com/RLadiesGlobal?ref_src=twsrc%5Etfw">@RLadiesGlobal</a> <a href="https://twitter.com/RLadiesBrisbane?ref_src=twsrc%5Etfw">@RLadiesBrisbane</a> <a href="https://twitter.com/RLadiesSydney?ref_src=twsrc%5Etfw">@RLadiesSydney</a> <a href="https://twitter.com/RLadiesIstanbul?ref_src=twsrc%5Etfw">@RLadiesIstanbul</a> <a href="https://twitter.com/RLadiesIzmir?ref_src=twsrc%5Etfw">@RLadiesIzmir</a> <a href="https://twitter.com/RLadiesAKL?ref_src=twsrc%5Etfw">@RLadiesAKL</a> <a href="https://twitter.com/RLadiesDC?ref_src=twsrc%5Etfw">@RLadiesDC</a> <a href="https://twitter.com/RLadiesRemote?ref_src=twsrc%5Etfw">@RLadiesRemote</a> <a href="https://twitter.com/RLadiesMVD?ref_src=twsrc%5Etfw">@RLadiesMVD</a> <a href="https://twitter.com/hashtag/rladies?src=hash&amp;ref_src=twsrc%5Etfw">#rladies</a> <a href="https://twitter.com/hashtag/useR2018?src=hash&amp;ref_src=twsrc%5Etfw">#useR2018</a> <a href="https://twitter.com/hashtag/rstat?src=hash&amp;ref_src=twsrc%5Etfw">#rstat</a> <a href="https://t.co/aZoSuAU0Gi">pic.twitter.com/aZoSuAU0Gi</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1016604921154584576?ref_src=twsrc%5Etfw">July 10, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

We also managed to organise a gathering lunch of R-Ladies and conference newbies to give support to new comers to R and to people that came alone to the conference. A super R-Ladies cake was also there for the occasion!

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Thanks all of the amazing women coming around to R-ladies <a href="https://twitter.com/hashtag/useR2018?src=hash&amp;ref_src=twsrc%5Etfw">#useR2018</a> lunch today! <a href="https://t.co/7cwJUZi8mg">pic.twitter.com/7cwJUZi8mg</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1016883039241043973?ref_src=twsrc%5Etfw">July 11, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>



<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">R-ladies lunch at room P11! Come and join us! <a href="https://twitter.com/hashtag/useR2018?src=hash&amp;ref_src=twsrc%5Etfw">#useR2018</a> <a href="https://t.co/bqvGb7CmPv">pic.twitter.com/bqvGb7CmPv</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1016875124610351104?ref_src=twsrc%5Etfw">July 11, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


## We love our R babies

For the first time the conference was held in our emispehere and this gave us the opportunity to actively contributed to it under Di Cook's direction. Some of us organisers helped with some parts of the organisations like reviewing abstracts and scholarship applications or organising the childcare for the conference. Göknur Giner, one of the initial founder of the R-Ladies Melbourne,  helped with the childcare organisation and thanks to it she was able, like other parents, to attend the conference with her baby and letting her of to childcare to listen to talks and tutorials when needed. This is an opportunity that every conference should offer! Imagine how many amazing parents you keep missing out if we don't?

<blockquote class="twitter-tweet" data-lang="en"><p lang="und" dir="ltr"><a href="https://twitter.com/hashtag/hexwall?src=hash&amp;ref_src=twsrc%5Etfw">#hexwall</a> <a href="https://twitter.com/hashtag/useR2018?src=hash&amp;ref_src=twsrc%5Etfw">#useR2018</a> <a href="https://twitter.com/hashtag/maya?src=hash&amp;ref_src=twsrc%5Etfw">#maya</a> <a href="https://twitter.com/hashtag/childfriendlyconferences?src=hash&amp;ref_src=twsrc%5Etfw">#childfriendlyconferences</a> <a href="https://t.co/JN55krtZe5">pic.twitter.com/JN55krtZe5</a></p>&mdash; Göknur Giner (@goknurginer) <a href="https://twitter.com/goknurginer/status/1017362105949802497?ref_src=twsrc%5Etfw">July 12, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## CSL supports gives us more than money!

As R-Ladies we had the chance to sponsor the conference providing two $500 scholarships which allowed two R-Ladies living in Melbourne, Dewi Angraini and Lucy Liu, to take part to the conference. Increasing gender and diversity balance at R conferences is, after all, one of the core aims of the whole R-Ladies movement. Having the chance to actively contribute to it made us feels super powerful and hopeful! We are enourmously thankful to our sponsor [CSL](https://www.csl.com/) from Melbourne which is giving us this and many other opportunities to grow and pursue the change in which we believe. Below are the two enthusiastic R-Ladies who were granted the scholarships. They also shared with us below a few words about what that travel grant meant for them!

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Congratulations again to the two winners of our scholarship for <a href="https://twitter.com/hashtag/useR2018?src=hash&amp;ref_src=twsrc%5Etfw">#useR2018</a> <a href="https://twitter.com/lucyleeow?ref_src=twsrc%5Etfw">@lucyleeow</a> and Dewi, finally here, with all the rest! <a href="https://t.co/3Q94qAaVjt">pic.twitter.com/3Q94qAaVjt</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1016892581483954176?ref_src=twsrc%5Etfw">July 11, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

**Lucy's useR! 2018**

*"Would like to thank the RLadies Melbourne group for offering me a scholarship to attend the useR!2018 conference. The conference was an amazing showcase of the wide range of fields where R is used and the diversity of R users. The R community is known for being welcoming and diverse and the conference gave me a great opportunity to network these talented people. The interesting discussion on the variety of simple ways to help the community (e.g. via editing documentation, offering to write vignettes) has also inspired me to start contributing. I would not have been able to attend without the help of this scholarship and I am very grateful."* 

**Dewi's useR! 2018**

*"As a person who has background of Mathematics and Statistics, I thought I was too late to learn R and it was embarrassing that I just started learning R in the final year of my PhD. However, my great passion and intention to bring the knowledge of R back to my home country and teach my students about R has been significantly appreciated by the R-Ladies Melbourne by granting me the domestic travel scholarship to attend useR! 2018 in Brisbane. The conference gave me chance to engage with people from the R community from different countries, including  my home country Indonesia, and pushed me to further enlarge the R community in Indonesia which apparently remains limited, particularly in rural areas. I put a big hope that R-Ladies Melbourne can continuously support us in initiating the expansion of R community in Indonesia".*


# Two years anniversary

## Lightning talks and the best R prices!

To celebrate the special occasion we organised the first series of lightning talks where we asked our members to share with us their favourite R tips! They are now all collected and showcased together here https://rladies-melbourne-tips.netlify.com/ (strongly suggest to check it out!)! Since then, I still go through it sometimes and I started using interesting features like the `DT::datatable` to dispaly tables on HTML pages allowing for filtering, sorting and easy searching!

This sounds all very exiting, but really, at first and almost until the last a few days we weren't really sure that it was going to work. We didn't have any submission for lighning talks until the last three days. And this is not because people are lazy! When you organise events and you hope to attract volunteers to speak at evening events which are not official conferences and after a hard day at work... you need to realise that it can be a big thing to ask! However, we didn't give up and that was the most important thing. We supported each other, we knew we might have had to share something ourselves as organisers and we just kept trying! When you try to organise something new don't give up. Do everything that you can to keep your plan and your initial idea going. Most times, I believe, you will be rewarded. Indeed, in the end we were extremenly happy to see enthusiatic young women come and share their expertise with all of us. We must admit that we also had amazing 3D printed R earrings to attract speakers!

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">😮 Did you know you could win 🏆 these fab 💃 uniquely made eaRRings (purple 💜 available on the night!)? How 😏 ?! Submit 💻 your favourite <a href="https://twitter.com/hashtag/R?src=hash&amp;ref_src=twsrc%5Etfw">#R</a> tip to <a href="https://t.co/QI8F3FPAti">https://t.co/QI8F3FPAti</a> and present 🎬 it at our next event! Email also works! See here for more details <a href="https://t.co/M9nuKHWsVx">https://t.co/M9nuKHWsVx</a> <a href="https://t.co/vqSB2SJ9vT">pic.twitter.com/vqSB2SJ9vT</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1047270616087162880?ref_src=twsrc%5Etfw">October 2, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

## Panel discussion

After the talks we also organised our first panel discussion with four R-Ladies from Melbourne at different stages of their career: Belinda Maher from Transport for Victoria, Nikki Rubinstein from PwC and Melissa Davis from Walter and Eliza Hall Institute.


<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Great <a href="https://twitter.com/RLadiesMelb?ref_src=twsrc%5Etfw">@RLadiesMelb</a> Sesh! So many awesome tips! <a href="https://t.co/J4Qiv3CcYZ">pic.twitter.com/J4Qiv3CcYZ</a></p>&mdash; Brigitte Lewis (@briglewis) <a href="https://twitter.com/briglewis/status/1052469031188353024?ref_src=twsrc%5Etfw">October 17, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

We asked them about their R workflows and suggestions about public speaking. Melissa suggested that the type of workflows adopted within her lab strongly depends on whether the research is aimed at exploratory analysis or method implementation and how they found super useful the `pkgdown` package to showcase and share packages developed in her lab. She also suggested that in her early career as researchers she was actively volunteering to give talks at different seminars for her research to be heard by a wider audience and that this strategy really helped making her voice heard and her contribution being recognised in her field. Nikki's advice was to remember that when you are giving a public talk you need make sure that the first thing the audience knows is why they should care about what you are telling them. You need to get their attention! Also Nikki's go-to workflow is to set up a new R project for a new analysis and link it to a git repository, creating an organised folder structure for data, analysis files, reports and figures.
The speakers also commented about the importance of always celebrating achievements! Nikki's favourite celebration is going for frozen yoghurt! What's yours?! 


# First `#rstats` online lunch meetup

Mid November, Soroor Hediyeh Zadeh suggested the great idea of starting an `#rstats` seminar series that we could held as alternative or together with our monthly evening and longer meetups. Several members already asked us to run morning or lunch events to come towards other people's and families needs. Well, there was the opportunity! Soroor raised the suggestion that these lunch seminars would be more focused on Statistics theory with, of course, R implementation. 
Initially we were worried that we couldn't find a place with such a short notice to host an event and that it might be hard for people to reach it when only a lunch break is available. That's when we decided to try our first online Zoom meetup! That cut any cost and worries for us and allowed everyone to reach us in a click sitting at their desk. While Soroor was presenting we muted the sound coming from every participant connected to the call to avoid background noise. Participants were still able to ask questions via the Zoom chat. It was our first online experiment and we did agree that it was a brilliant and successful one!
If felt different and also we are still not sure how many people we are able to have in the same Zoom chat at once but it gave us the chance to quickly setup a meetup without the need to find a space and at no cost! Of course, the drawback is that you loose a bit the networking part of the meetup since it gets harder to netwrok online especially if you have a few people connected at the same time. I believe that alternating such events is key. We hope this will give the chance to a different audience to actively participate to the events and ask questions and not just watching recorded events by themselves. 


<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr"><a href="https://twitter.com/hashtag/nonparametric?src=hash&amp;ref_src=twsrc%5Etfw">#nonparametric</a> vs <a href="https://twitter.com/hashtag/parametric?src=hash&amp;ref_src=twsrc%5Etfw">#parametric</a> models in <a href="https://twitter.com/hashtag/R?src=hash&amp;ref_src=twsrc%5Etfw">#R</a> by <a href="https://twitter.com/SoroorHediyeh?ref_src=twsrc%5Etfw">@SoroorHediyeh</a> through <a href="https://twitter.com/hashtag/zoom?src=hash&amp;ref_src=twsrc%5Etfw">#zoom</a> <a href="https://twitter.com/hashtag/online?src=hash&amp;ref_src=twsrc%5Etfw">#online</a> <a href="https://twitter.com/hashtag/rstat?src=hash&amp;ref_src=twsrc%5Etfw">#rstat</a> <a href="https://twitter.com/hashtag/RLadies?src=hash&amp;ref_src=twsrc%5Etfw">#RLadies</a> <a href="https://t.co/AisVGnvjez">pic.twitter.com/AisVGnvjez</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1070122679238180865?ref_src=twsrc%5Etfw">December 5, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


# Our everyday life tips as the R-Ladies Melbourne team going towards not-profit status

In the last part of the post, I would like to change the perspective and instead of talking about events and things that we did, I will talk about what goes behind the scene and HOW we did it. 

Becoming a not-for-profit and then eventually a charity was R-Ladies Globale 2018 goal

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">CALLING ALL <a href="https://twitter.com/hashtag/RLadies?src=hash&amp;ref_src=twsrc%5Etfw">#RLadies</a>  <a href="https://twitter.com/hashtag/RLadiesSupporters?src=hash&amp;ref_src=twsrc%5Etfw">#RLadiesSupporters</a> 💜🌎🌍🌏 PLEASE SHARE 💬 <a href="https://twitter.com/RLadiesGlobal?ref_src=twsrc%5Etfw">@RLadiesGlobal</a> needs your help💪 ! Our goal🏆 for #2018 is to become a charitable organisation 🎉.If you or someone you know can provide specialist help please email📩 leadership@rladies.org <a href="https://t.co/ua4sRDbGPz">https://t.co/ua4sRDbGPz</a> <a href="https://t.co/fCDfUQreAM">pic.twitter.com/fCDfUQreAM</a></p>&mdash; R-Ladies Global (@RLadiesGlobal) <a href="https://twitter.com/RLadiesGlobal/status/969497293647962112?ref_src=twsrc%5Etfw">March 2, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

The process of becoming a registered association depends, however, from each country's rules and this is whay we had to understand ourselves how to accomplish this in Australia. One thing also sure, becoming a registered association does require the group to have a defined structure. Before talking about the actual burocratic path that we are following I would like to mention about the daily journey that we are going through as R-Ladies Melbourne organisers. 

Between 2017-2018 we still orgnanised an event once a month and with a growing community it can become challenging especially when you have a job, a PhD to do, a newborn or any other life committment. This of course, would be the same across every R-Ladies groups across the world where generous people put aside part of their free time for the bigger cause! This is why I would like to share a bit about how R-Ladies Melbourne deals with the day to day committements and how we managed so far to keep our community going. I believe this might be of interest for other groups or other organisations, not only R-ladies.

Also, we always appreciate any feedback! 

## R-Ladies Global guidelines: the active centralised support that makes the difference

The first indispensable component is the R-Ladies Global organisation and their [support and guidelines](https://github.com/rladies/starter-kit) for starting and leading R-Ladies chapters in a new city. Thanks to their guidelines, continuous prompt support and the extended global Slack community we really can never feel left alone at our destiny! Whenever we need someone to talk to we can count on a thrieving R-Ladies slack channel that brings organisers and members next to each other. On this note, I would like to mention the R-Ladies [Slack community](http://rladies-community-slack.herokuapp.com) that brings together women and gender minorities from around the worls and you don't to be an organiser to be oart of it.

I found really interesting the article [Why Women Are Flourishing In R Community But Lagging In Python](https://reshamas.github.io/why-women-are-flourishing-in-r-community-but-lagging-in-python/) written by Reshama. She is an organiser of the [NYC Women in Machine Learning and Data Science (WiMLDS)](https://www.meetup.com/NYC-Women-in-Machine-Learning-Data-Science/) and [NYC PyLadies](https://www.meetup.com/NYC-PyLadies/) and she suggests that having a centrilised active board like there is for the R-ladies and for WiMLDS makes it so much better to support chapters around the world.


## Support each other and offer your support to your R-Ladies local group

From a local community point of view, the key component is the support that we give each other. We are never alone! Since the beginning, we were a group of eigth enthusiastics friends-colleagues that understood everyone elses needs and shared the same passion for R. Eight people might seems like a large number but this means that when someone of is going through busier or tougher periods they know they can ask someone else to take over R-Ladies duties. Of course, this is not the lucky case for many other groups. Therefore, if you know that a new R-Ladies chapter in your city has started, you can also be sure that they might need help! I spoke with a few other organisers (from Australia, New Zealand and the US) and most of them do a lot of the hard work alone or with very few helpers. Organising is hard and you can be sure that your help would be hugely appreciated!


## Define rules and tasks

This year's R-Ladies Global goal was to become a not-for-profit association. The process varies from country to country and having rules defined for your own group combined with the R-Ladies Global guidelines is a good start and you will need it! 
We are all learning to become little leaders as we go. This year in particular, we have been trying to establish more structure in our organising committee. We hold monthly meetings where we try to stay on track with monthly committments and events as well as to think about long-term plans, sponsorships, new ideas for the future and new things that are happening in the R community. 
As I mentioned, defining roles and positions is necessary when you start thinking about becoming a not-for-profit association. There are fixed roles, like a president, vice-president, secretary and treasurer that are required in any organisation and then there are roles that we setup and will elect every year, like the social media and the event planning responsibles. We established that every month in turn one organiser is responsible to supervise the organisation of the event and we wrote down specific tasks that the event organiser should remember and is responsible for. This is all work in progress but it has been really useful to get it started and to help us split time and people between tasks. Below are the faces and roles that we assigned in 2018! We had three new addition to the group mid this year (Nikki Rubinstein, Lucy Liu and Adele Barughase) who haven't been assigned a specific role yet. 


```{r fig.cap = "Organisers between 2017 and 2018"}
img <- readPNG("AllPhotos/organisers.png")
grid.raster(img)
```



## Be ready to pass the ball

Our structure is still far away from being perfect, there is still a lot of work to do and our organisation doesn't work always as smoothly as we envisioned. However, we are really working hard towards making the R-Ladies Melbourne management accessible to new organising members. This is because we should be able to pass the ball to new volunteers who can bring fresh ideas to the team. We are all at different stages of our careers, we might have different plans for the coming future but we all want the R-Ladies Melbourne to keep thriving. 

## Support from our sponsors

Since the beginning we have been super lucky to see our hard work and enthusiasm being supported with actual funding. Unfortunately, love cannot pay for everything! Hosting events, attracting people and supporting for conferences, just to mention some, come at a cost. Since our birth in 2016 we have been having faithful support from [CSL](https://www.csl.com/) and [Zendesk](https://www.zendesk.com/). Zendesk allowed us to use their amazing space to host our events and provided us with drinks and food for more than a year. Occasionally, we hosted our events at the [Walter and Eliza Hall Institute](https://www.wehi.edu.au/) or rented spaces for weekend workshops at the [Kathleen Syme Library](https://www.melbourne.vic.gov.au/community/hubs-bookable-spaces/kathleen-syme-library-and-community-centre/Pages/kathleen-syme-library.aspx). Recently, thanks to being at useR! 2018 we found a new sponsor, [Nous Group](https://www.nousgroup.com/uk-home/), whose principal [David Diviny](https://www.nousgroup.com/people/david-diviny/) approached us and asked how they could support our events in the future! Now Nous Group offers us a an amazing free room in the CBD in their offices with the most beautiful Melbourne view to hosts our events every second months, alternating with Zendesk. Thanks to CSL funds we could cover the costs of renting locations or other expenses, like paying for security or refreshments. Just recently, CSL has agreed to sponsor us for the coming two years!! Having those funding will allow us to focus our attentions, at least for a while, on improving and organising diverse events.

# Become a not-for-profit in Australia

As I mentioned before, different lows applies to different countries. Even within Australia, different laws applies to differen states. I initially found it really useful to read through the material provided by the [nfplaw](https://www.nfplaw.org.au/) website. Here you can find plently of information about what is means to incorporate and it guides you through the understanding of whether you should consider incorporating. Everything is explained in a very easily accessible manner so you don't need to be a lawyer to get through it.
Since our group will have to comply with the Victorian laws we are now following the [Consumer Affair Victoria](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/become-an-incorporated-association) rules. It was easy enough for us with no law background to understand what steps to take.


# Become our speaker! - How to contact us


We are always looking for new speakers for seminars, workshops, other ideas! If you have an idea for an event and you want to share it with us and other R passionate, we would love to hear from you! 

You can use any of the means below to contact us!

* `r icon::fa("twitter",colour = "#88398A")` https://twitter.com/RLadiesMelb
* `r icon::fa("github",colour = "#88398A")` https://github.com/R-LadiesMelbourne
* `r icon::fa("meetup",colour = "#88398A")` https://www.meetup.com/R-Ladies-Melbourne/
* `r icon::fa("facebook",colour = "#88398A")` https://www.facebook.com/RladiesMelbourne/
* Email: melbourne@rladies.org


# Testimonial from a past speaker: Belinda Maher



Belinda Maher was our speaker in [February 2018](https://www.youtube.com/watch?v=84G6ZNTEHCo&t=345s) and we also invited her for the panel discussion in October. Below you can find Belinda's thoughts on how being a speaker at our event helped her gaining confidence in herself and her skills!

*Presenting at R Ladies helped me to consider the audience's point of view: to think about exactly what was interesting and important about my work, and what needed further explanation for an audience who are not already familiar with the topic. I also gained presenting experience and had to think about how to change the content of my presentation to suit a less transport-focused audience than I am used to. While I notice that I sounded nervous at the start of my presentation, I would not hesitate to present my work again to a large group. The success of the presentation gave me confidence that I am quite capable of presenting and that it won’t be a disaster! Confidence that I will actually probably get good feedback if I present again. I discovered that it’s quite easy to talk about something which you’re passionate about. The networking opportunities which speaking at R Ladies has given me have also been a bonus. It’s nice also casually drop in to conversation when talking about my work: "oh, I did a presentation on that to 70 people at a user group, it’s on YouTube!"*
 

# References

To produce this document I used some of the tips in [Pimp my Rmd](https://holtzy.github.io/Pimp-my-rmd/#use_dt_for_tables) by [Yan Holtz](https://github.com/holtzy)


