---
title: "Everyday life tips as the R-Ladies Melbourne team"
author: "Anna Quaglieri, 2018 Main organiser"
date: "January 2019"
output:
  html_document:
    includes:
      after_body:
      - header.html
      - footer.html
    theme: cosmo
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(magick)
library(png)
library(grid)
library(emo)
library(icon)
```

# How everything started: the importance of conferences, travel grants and Twitter!

The R-Ladies Melbourne chapter was founded in September 2016 by [Göknur Giner](https://twitter.com/goknurginer) and [Sepideh Foroutan](https://twitter.com/S_Foroutan). Thanks to a travel scholarship granted by the Walter and Eliza Hall Institute, Göknur could travel to Stanford to attend her first useR! conference in 2016. That's when she found out about everything that was happening around the R-Ladies movement. Sepideh found out about the R-Ladies via Twitter and the same idea rose in their minds: start an R-Ladies group in Melbourne! Together with [Roxane Legaie](https://twitter.com/RoxaneLegaie), [Saskia Freytag](https://twitter.com/trashystats), Alex Garnham, [Soroor Zadeh](https://twitter.com/SoroorHediyeh) and [myself](https://twitter.com/annaquagli) the first committee meeting was setup at the Walter and Eliza Hall Institute and the [launch event](https://www.meetup.com/R-Ladies-Melbourne/events/234683544/) took place in October! [Marie Trussart](https://twitter.com/MTrussart) joint in December of the same here.

My memories of that first meeting are both very exciting and vague. At the beginning, we didn't really know exactly where we would have gone from there or how much we would have grown but we were all extremely excited about starting something new, together, and for which we all shared a great passion! 

Like a lot of new groups we did not have defined roles for the first year, but everyone just helped out depending on how much they could. That is to say that so it is OK to initiate a group without clear roles and then gradually it can be developed! Göknur did an amazing job setting up all the necessary infrastructure to get us started with the [Meetup page](https://www.meetup.com/R-Ladies-Melbourne/), Twitter and the email account. She got all of us on Slack and helped defining the final R-Ladies logo. 

Between 2016-2018 we orgnanised an event once a month apart from the months of Janaury. With a growing community it can become challenging, especially when you have a job, a PhD to write, a newborn, or any other life committment. This of course, would be the same across every R-Ladies group across the world where generous people put aside part of their free time for  worthy cause! This is why I would like to share a bit about how we deal with the day to day commitments and how we have so far managed to keep our community going. I believe this might be of interest to other groups or organisations, and not just R-ladies.

# R-Ladies Global guidelines: the active centralised support that makes the difference

The first indispensable component is the R-Ladies Global organisation and their [support and guidelines](https://github.com/rladies/starter-kit) for starting and leading R-Ladies chapters in a new city. Thanks to their guidelines, continuous prompt support and the extended global Slack community we really never feel that we’re left to our own devices…in a figurative sense! Whenever we need someone to talk to we can count on a thriving R-Ladies slack channel that brings organisers and members together. On this note, I would like to mention the R-Ladies [Slack community](http://rladies-community-slack.herokuapp.com) that brings together women and gender minorities from around the world; and you don’t need to be an organiser to be part of it.

I found the article [Why Women Are Flourishing In R Community But Lagging In Python](https://reshamas.github.io/why-women-are-flourishing-in-r-community-but-lagging-in-python/) written by Reshama really interesting. She is an organiser of the [NYC Women in Machine Learning and Data Science (WiMLDS)](https://www.meetup.com/NYC-Women-in-Machine-Learning-Data-Science/) and [NYC PyLadies](https://www.meetup.com/NYC-PyLadies/) and she suggests that having a centralised and active board, like that for R-ladies and for WiMLDS, makes it so much easier to support chapters around the world.

# Support each other and offer your support to your R-Ladies local group

From a local community point of view, the key component is the support that we give each other. We are never alone! Since the beginning, we were a group of eight enthusiastic friends-colleagues that understood everyone else’s needs and shared the same passion for R. Eight people might seem like a large number but this means that when one of us is going through a busier or tougher period they know that they can count on someone else to take over R-Ladies duties. Of course, this is not the lucky case for many other groups. Therefore, if you know that a new R-Ladies chapter has started in your city, you can also be sure that they might need your help! I spoke with a few other organisers (from Australia, New Zealand, US and Argentina) at the useR! 2018 conference and via email and most of them do a lot of the hard work alone or with very few helpers. **Organising is hard and you can be sure that your help would be hugely appreciated!**

# Define rules and tasks

Becoming a not-for-profit and then eventually a charity was R-Ladies Globale 2018 goal.

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">CALLING ALL <a href="https://twitter.com/hashtag/RLadies?src=hash&amp;ref_src=twsrc%5Etfw">#RLadies</a>  <a href="https://twitter.com/hashtag/RLadiesSupporters?src=hash&amp;ref_src=twsrc%5Etfw">#RLadiesSupporters</a> 💜🌎🌍🌏 PLEASE SHARE 💬 <a href="https://twitter.com/RLadiesGlobal?ref_src=twsrc%5Etfw">@RLadiesGlobal</a> needs your help💪 ! Our goal🏆 for #2018 is to become a charitable organisation 🎉.If you or someone you know can provide specialist help please email📩 leadership@rladies.org <a href="https://t.co/ua4sRDbGPz">https://t.co/ua4sRDbGPz</a> <a href="https://t.co/fCDfUQreAM">pic.twitter.com/fCDfUQreAM</a></p>&mdash; R-Ladies Global (@RLadiesGlobal) <a href="https://twitter.com/RLadiesGlobal/status/969497293647962112?ref_src=twsrc%5Etfw">March 2, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

The process of becoming a registered association depends on each country’s laws and this is why we had to understand how to accomplish this in Australia. Firstly, becoming a registered association requires the group to have a defined structure. Having rules defined for your own group combined with the R-Ladies Global guidelines is a good start and you will need it.
We are all learning to become little leaders as we go. This year in particular, we have been trying to establish more structure in our organising committee. We hold monthly meetings where we try to stay on track with monthly committments and events as well as think about long-term plans, sponsorships, new ideas for the future and new things that are happening in the R community. As I mentioned, defining roles and positions is also necessary when you start thinking about becoming a not-for-profit association. There are fixed roles, like a president, vice-president, secretary and treasurer that are required in any organisation as specified by the Consumer Affair Victoria [model rules](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/running-an-incorporated-association/rules) for an incorporated association. Then, there are roles that we set up as we need them, such as the social media and event planning responsibilities. We established that every month, in turn, one organiser is responsible to supervise the organisation of the event and we wrote down specific tasks that the event organiser should remember and is responsible for. This is all work in progress but it has been really useful to get us started and to help us split time and people between tasks. Below are the faces and roles that we assigned in 2018! We had three new additions to the group halfway through the year (Nikki Rubinstein, Lucy Liu and Adele Barughase) who haven’t been assigned a specific role yet.


```{r fig.cap = "Fig1. Organisers between 2017 and 2018"}
img <- readPNG("AllPhotos/organisers.png")
grid.raster(img)
```


# Be ready to pass the ball

Our structure is still far away from being perfect; there is still a lot of work to do and our organisation doesn’t always work as smoothly as we envisioned. However, we are really working hard towards making the R-Ladies Melbourne management accessible to new organising members. This means having written rules that new people can refer to, for example, is really useful. This is because we should be able to pass the baton to new volunteers who can bring fresh ideas to the team. We are all at different stages of our careers, and we might all have different plans for the future but we all want the R-Ladies Melbourne to keep thriving. 

# Finding sponsors

From the beginning we have been super lucky to see our hard work and enthusiasm being supported with actual funding. Unfortunately, love cannot pay for everything! Hosting events, attracting people and support for conferences, just to mention a few things, come at a cost. Since our birth in 2016 we have been faithfully supported by [CSL](https://www.csl.com/) and [Zendesk](https://www.zendesk.com/). Zendesk allowed us to use their amazing space to host our events and have been providing us with drinks and food for over a year. Occasionally, we hosted our events at the [Walter and Eliza Hall Institute](https://www.wehi.edu.au/) or rented spaces for weekend workshops at the [Kathleen Syme Library](https://www.melbourne.vic.gov.au/community/hubs-bookable-spaces/kathleen-syme-library-and-community-centre/Pages/kathleen-syme-library.aspx). Recently, thanks to being at useR! 2018 we found a new sponsor, [Nous Group](https://www.nousgroup.com/uk-home/), whose principal [David Diviny](https://www.nousgroup.com/people/david-diviny/) approached us and asked how they could support our events in the future! Now Nous Group offers us a an amazing free room in the CBD in their offices with the most beautiful Melbourne view to hosts our events every second month, alternating with Zendesk. Thanks to CSL funds we could cover the costs of renting locations or other expenses, like paying for security or refreshments. Just recently, CSL has agreed to sponsor us for the coming two years!! Having that funding will allow us to focus our attention, at least for a while, on improving and organising diverse events.

For some time, we were not sure if we were going to have funding and there are other opportunities that groups might want to look into:

* The R Consortium's R User Group grants  https://www.r-consortium.org/projects/r-user-group-support-program
* Asking local businesses and organisations in your area. On this note, I was able to ask for fundraising advice from the institute where we work (Walter and Eliza Hall Institute). What we were suggested to do was to have a little presentation/flyer ready about our group, who we are, why our existence is important and how we could be beneficial for a potential sponsor (e.g. their employees can actually benefit and learn from our events). Then, try to target a few places to send (via email but preferably in person) the sponsorship requests and see how it goes. We have not had to do this yet but we want to be ready for it.  
* Apply for various diversity grants. However, a few of them that we were interested in, only sponsor actual registered associations. Hence the reason why we are working towards it.
* Ask on the R-Ladies Slack for more help! That is, for example, how I found out about the R Consortium’s R User Group grants!

# Finding speakers

Here is where creating and growing our network is really beneficial! Melbourne is a big city, but still, with a lot of us organisers working in academia, it can become hard to diversify seminars and workshops. We initially brainstormed ideas for potential speakers, a lot of them suggested by the amazing Di Cook! Then, we tried to contact them and see when they might be available, and therefore plan our year of events. Plans might change if we know that some speakers are in town due to conferences, as occurred last August with Emi Tanaka visiting from Sydney. Also, continuously reminding that we are looking for speakers at every events or posting it on Twitter really helped!! So far, we haven’t had a defined structure behind the events, like a theme underlying our choices. We worked around speakers’ availability and diversity. To guide us through decisions we sent around a survey at the beginning of 2018 askying our members what they would like to see and tried to follow those requests. You can find more about the survey in the [introduction talk](https://docs.google.com/presentation/d/1WKIw9l4LfMaf3eY7KTHDCqlV0wHLfXB9NdcR68JGpNE/edit?usp=sharing) that I gave for our anniversary in October. In general, we try to organise some more introductory and some more advanced topics to allow different people to come along. At the end of 2018, one of the organisers, Soroor, suggested we start an #rstats lunch seminar series with a more statistical background theme!

# Become a not-for-profit in Australia


As I mentioned before, different laws apply to different countries. Even within Australia, laws vary between the states. I initially found it really useful to read through the material provided by the [nfplaw](https://www.nfplaw.org.au/) website. Here, you can find plenty of information about what it means to incorporate and it guides you through understanding whether you should consider incorporating. Everything is explained in a very easily accessible manner so you don’t need to be a lawyer to get through it. Since our group will have to comply with the Victorian laws we are now following the [Consumer Affair Victoria](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/become-an-incorporated-association) rules and it was easy enough for us, with no law background, to understand what steps to take.

# Get involved and share your ideas! - How to contact us
  
If there is something else that you would like to know but I haven't discussed here please feel free to send us an email at Email: melbourne@rladies.org. 
Also, we are always looking for new speakers for seminars, workshops and new ideas! And ff you would like to get involved as organiser or in other ways, we would love to hear from you.
  
You can use any of the means below to contact us:
  
* `r icon::fa("twitter",colour = "#88398A")` https://twitter.com/RLadiesMelb
* `r icon::fa("github",colour = "#88398A")` https://github.com/R-LadiesMelbourne
* `r icon::fa("meetup",colour = "#88398A")` https://www.meetup.com/R-Ladies-Melbourne/
* `r icon::fa("facebook",colour = "#88398A")` https://www.facebook.com/RladiesMelbourne/
* Email: melbourne@rladies.org


# Aknowledgements

* To produce this document I used some of the tips in [Pimp my Rmd](https://holtzy.github.io/Pimp-my-rmd/#use_dt_for_tables) by [Yan Holtz](https://github.com/holtzy)
* Thanks to my friend Steven for proof reading my first blog post! Thanks to Saskia, Sepideh and Marie for their helpful suggestions!