---
title: "Everyday life tips as the R-Ladies Melbourne team"
author: "Anna Quaglieri, 2018 Main organiser"
date: "January 2019"
output:
  html_document:
    includes:
      after_body:
      - header.html
      - footer.html
    theme: cosmo
    toc: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(magick)
library(png)
library(grid)
library(emo)
library(icon)
```

# How everything started: the importance of conferences, travel grants and Twitter!

[R-Ladies](https://rladies.org/) is a world-wide organisation founded in San Francisco by [Gabriela de Queiroz](https://k-roz.com/) with the aim of promoting gender diversity within the [R](https://www.r-project.org/) community.

As the first R-Ladies chapater in Australia, the R-Ladies Melbourne was founded in September 2016 by [Göknur Giner](https://twitter.com/goknurginer) and [Sepideh Foroutan](https://twitter.com/S_Foroutan). Thanks to a travel scholarship granted by the Walter and Eliza Hall Institute, Göknur could travel to Stanford to attend her first useR! conference in 2016. That's when she found out about everything that was happening around the R-Ladies movement. Sepideh found out about the R-Ladies via Twitter and the same idea rose in their minds: start an R-Ladies group in Melbourne! Together with [Roxane Legaie](https://twitter.com/RoxaneLegaie), [Saskia Freytag](https://twitter.com/trashystats), [Alexandra Garnham](https://www.wehi.edu.au/news/illuminate-newsletter/december-2014/staff-profile-ms-alexandra-garnham), [Soroor Zadeh](https://twitter.com/SoroorHediyeh) and [myself](https://twitter.com/annaquagli) the first committee meeting was setup at the Walter and Eliza Hall Institute and the [launch event](https://www.meetup.com/R-Ladies-Melbourne/events/234683544/) took place in October! [Marie Trussart](https://twitter.com/MTrussart) joint in December of the same year. Since then, new groups have started in Adelaide, Sydney and Canberra!

My memories of that first meeting are both very exciting and vague. At the beginning, we didn't really know exactly where we would have gone from there or how much we would have grown but we were all extremely excited about starting something new, together, and for which we all shared a great passion! 

Like a lot of new groups we did not have defined roles for the first year, but everyone just helped out depending on how much they could. That is to say, that it is OK to initiate a group without clear roles and then gradually it can be developed! Göknur did an amazing job setting up all the necessary infrastructure to get us started with the [Meetup page](https://www.meetup.com/R-Ladies-Melbourne/), Twitter and the email accounts. She got all of us on Slack and helped defining the final R-Ladies logo. However, towards the second half of 2017 when she became mum for the first time, I started taking over more and more responsibilities until we decided to establish more defined roles and I had the amazing opportunity to be elected (more or less officially) as the main organiser.

Between 2016-2018 we organised an event once a month apart from the months of Janaury. With a growing community it can become challenging to keep up with the events, especially when you have a job, a PhD to write, a newborn, or any other life committment. This of course, would be the same across every R-Ladies group across the world where generous people put aside part of their free time for worthy cause! That's why I decided, after more than two years of operating with the organising team, to sit down and write about how we deal with the day to day commitments and how we have so far managed to keep our community going. I believe this might be of interest to other groups or organisations, not just R-ladies.

# R-Ladies Global guidelines: the active centralised support that makes the difference

The first indispensable component is the R-Ladies Global organisation and their [support and guidelines](https://github.com/rladies/starter-kit) for starting and leading R-Ladies chapters in a new city. Thanks to their guidelines, continuous prompt support and the extended global Slack community we never feel that we’re left to our own devices... in a figurative sense! Whenever we need someone to talk to we can count on a thriving R-Ladies slack channel that brings organisers and members together. On this note, I would like to mention the R-Ladies [Slack community](http://rladies-community-slack.herokuapp.com) that brings together women and gender minorities from around the world; and you don’t need to be an organiser to be part of it.

I found the article [Why Women Are Flourishing In R Community But Lagging In Python](https://reshamas.github.io/why-women-are-flourishing-in-r-community-but-lagging-in-python/) written by Reshama really interesting. She is an organiser of the [NYC Women in Machine Learning and Data Science (WiMLDS)](https://www.meetup.com/NYC-Women-in-Machine-Learning-Data-Science/) and [NYC PyLadies](https://www.meetup.com/NYC-PyLadies/) and she suggests that having a centralised and active board, like that for R-ladies and for WiMLDS, makes it so much easier to support chapters around the world.

# Support each other and offer your support to your R-Ladies local group

From a local community point of view, the key component is the support that we give each other. We are never alone! Since the beginning, we were a group of eight enthusiastic friends-colleagues that understood everyone else’s needs and shared the same passion for R. Eight people might seem like a large number but this means that when one of us is going through a busier period they know that they can count on someone else to take over R-Ladies duties. Of course, this is not the lucky case for many other groups. Therefore, if you know that a new R-Ladies chapter has started in your city, you can also be sure that they might need your help! I spoke with a few other organisers (from Australia, New Zealand, US and Argentina) at the useR! 2018 conference and via email and most of them do a lot of the hard work alone or with very few helpers. **Organising is hard and you can be sure that your help would be hugely appreciated!**. 

# Finding sponsors

```{r fig.cap = "Fig2. Current R-Ladies Melbourne sponsors." , fig.asp = 0.2}
img <- readPNG("AllPhotos/current_sponsors.png")
grid.raster(img)
```


From the beginning we have been super lucky to see our hard work and enthusiasm being supported with actual funding. Unfortunately, love cannot pay for everything! Hosting events, attracting people and providing support for conferences, just to mention a few things, come at a cost. Since our birth in 2016 we have been faithfully supported by [CSL](https://www.csl.com/) and [Zendesk](https://www.zendesk.com/). [Melbourne Data Science](https://www.meetup.com/Data-Science-Melbourne/?chapter_analytics_code=UA-49664189-1) also offered initial  support which was fundamental to get us started. Zendesk allowed us to use their amazing space to host our events and have been providing us with drinks and food for over a year. Occasionally, we hosted our events at the [Walter and Eliza Hall Institute](https://www.wehi.edu.au/) or rented spaces for weekend workshops at the [Kathleen Syme Library](https://www.melbourne.vic.gov.au/community/hubs-bookable-spaces/kathleen-syme-library-and-community-centre/Pages/kathleen-syme-library.aspx) for which we had to pay some rental costs. Recently, thanks to being at useR! 2018 we found a new sponsor: [Nous Group](https://www.nousgroup.com/uk-home/). Nous Group's principal [David Diviny](https://www.nousgroup.com/people/david-diviny/) contacted us via Twitter and asked how they could support our events in the future! After a chat at the conference he offered to host some of our events at their space. How great is to go to conferences?! Now Nous Group offers us a an amazing room in the CBD in their offices with the most beautiful Melbourne view to host our events every second month, alternating with Zendesk. 


<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">We have this beautiful rainbow at <a href="https://twitter.com/hashtag/nous?src=hash&amp;ref_src=twsrc%5Etfw">#nous</a> today! <a href="https://t.co/0zBVPYDyvX">pic.twitter.com/0zBVPYDyvX</a></p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1042312927531827200?ref_src=twsrc%5Etfw">September 19, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


Thanks to CSL funds we could cover the costs of renting locations or other expenses, like paying for security or refreshments. Just recently, CSL has agreed to sponsor us for the coming two years!! Having that funding will allow us to focus most of our attention, at least for a while, on improving and organising diverse events.

However, for some time last year, we were not sure if we were going to have funding and we started looking for other opportunities. I put together below some ideas that we were looking into:

* The R Consortium's R User Group grants  https://www.r-consortium.org/projects/r-user-group-support-program
* Ask on the R-Ladies Slack for more help! For example, that is how I found out about the R Consortium’s R User Group grants.
* Ask local businesses and organisations in your area. On this note, I was able to ask for fundraising advice at the institute where I work (Walter and Eliza Hall Institute). We were suggested to have a little presentation/flyer ready about our group, with things like: who we are, why our presence is important and how we could be beneficial to a potential sponsor (e.g. their employees can actually benefit and learn from our events). Then, the aim would be to target a few places to send the sponsorship requests (via email but preferably in person). Fortunately, CSL came to help us and we didn't need to look for more sponsors yet, but it is a good idea to be prepared for that. 
* Apply and look for various diversity grants. One possible problem with this option is that they are often only open to registered associations. Hence, the reason why we are working towards becoming a not-for-profit association (see section [below](#not-for-profit)).


# Finding speakers

Here is where creating and growing your network is really beneficial! Melbourne is a big city, but still, with a lot of us working in academia, it can become hard to diversify seminars and workshops. We initially brainstormed ideas for potential speakers that we knew of and a lot of them were suggested by the amazing Di Cook! Then, we tried to contact them and see when they might be available, and therefore plan our year of events. Plans might change if we know that some speakers are in town due to conferences, as occurred last August with [Emi Tanaka](https://sydney.edu.au/science/people/emi.tanaka.php) visiting from Sydney. We usually remind at every events to our members that we are looking for speakers and I found it really successful to keep posting on Twitter. 

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">To everyone out there🙋, we are seeking speakers 🎤 for our next events in <a href="https://twitter.com/hashtag/Melbourne?src=hash&amp;ref_src=twsrc%5Etfw">#Melbourne</a> and we would love 💙 your help! We <a href="https://twitter.com/hashtag/R?src=hash&amp;ref_src=twsrc%5Etfw">#R</a> open to any topic and to speakers from any field! Strike us with your suggestion 💫</p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/1011880881768681472?ref_src=twsrc%5Etfw">June 27, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">To all the ladies: Who wants to give a talk about how to create an R package?</p>&mdash; R-Ladies Melbourne (@RLadiesMelb) <a href="https://twitter.com/RLadiesMelb/status/974179395509272577?ref_src=twsrc%5Etfw">March 15, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


That is how we got [Earo Wang](https://earo.me/) to talk about [building R packages](https://github.com/earowang/rladies-pkg) and [Fiona Milne](https://twitter.com/fionascottym) to tell us about [her work at Eliiza](https://github.com/R-LadiesMelbourne/2018-11-14_From-zero-to-data-science-hero-in-1-week)! A few of us also prepared workshops across the years (Soroor, myself, Saskia, Roxane, Nikki, Adele and Marie).

So far, we haven’t had a defined structure behind the events, like a theme underlying our choices. We worked around speakers’ availability and diversity. To guide our decisions we sent around a survey at the beginning of 2018 askying our members what they would like to see and tried to follow those requests. You can find more about the survey in the [introduction talk](https://docs.google.com/presentation/d/1WKIw9l4LfMaf3eY7KTHDCqlV0wHLfXB9NdcR68JGpNE/edit?usp=sharing) that I gave in occasion of our anniversary in October. In general, we try to organise a mixture between introductory and advanced topics as well on a diversity of topics, to allow different people to come along. At the end of 2018, one of the organisers, Soroor, suggested that we started an `#rstats` lunch seminar series with a more statistical perspective. So, stay tuned to see what will happen! You can find more about the events that we organised between 2017-2018 in [this post](https://rladiesmelb2018.netlify.com/).


# Define rules and tasks: towards not-for-profit {#not-for-profit}

Becoming a not-for-profit and then eventually a charity was R-Ladies Global goal for 2018.

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">CALLING ALL <a href="https://twitter.com/hashtag/RLadies?src=hash&amp;ref_src=twsrc%5Etfw">#RLadies</a>  <a href="https://twitter.com/hashtag/RLadiesSupporters?src=hash&amp;ref_src=twsrc%5Etfw">#RLadiesSupporters</a> 💜🌎🌍🌏 PLEASE SHARE 💬 <a href="https://twitter.com/RLadiesGlobal?ref_src=twsrc%5Etfw">@RLadiesGlobal</a> needs your help💪 ! Our goal🏆 for #2018 is to become a charitable organisation 🎉.If you or someone you know can provide specialist help please email📩 leadership@rladies.org <a href="https://t.co/ua4sRDbGPz">https://t.co/ua4sRDbGPz</a> <a href="https://t.co/fCDfUQreAM">pic.twitter.com/fCDfUQreAM</a></p>&mdash; R-Ladies Global (@RLadiesGlobal) <a href="https://twitter.com/RLadiesGlobal/status/969497293647962112?ref_src=twsrc%5Etfw">March 2, 2018</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

The process of becoming a registered association depends on each country’s laws and this is why we had to understand how to accomplish this in Australia. Firstly, becoming a registered association requires the group to have a defined structure. Having rules defined for your own group combined with the R-Ladies Global guidelines is a good start and you will need it.
We are all learning to become little leaders as we go and this year in particular, we have been trying to establish more structure in our organising committee. We hold monthly meetings where we try to stay on track with monthly committments and events as well as think about long-term plans, sponsorships, new ideas for the future and new things that are happening in the R community. 

In a registered association there are fixed roles, like a president, vice-president, secretary and treasurer that are req by the Consumer Affair Victoria [model rules](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/running-an-incorporated-association/rules) for associations in Victoria. Then, there aBut this will very likely apply to associations elsewhere. re roles that we set up as we needed them, such as the responsibiles for social media and event planning. 

We also established that each month, in turn, one committee member is responsible for the organisation of an event and we wrote down specific tasks. For example, they should contact the speaker, collect the bio and abstract and they should prepare and give the introduction for the event. They should also supervise all the necessary logistics for the events, like catering, location, flyer etc... This does not mean that they will do everything themselves but they should make sure that everything is on track. This is all work in progress and it has been possible for us since a relatively large group. It has been really useful to get us started and to help us rememremind usld split time and people between tasks, to avoid that one person ends up doing too much, which sometime, undoubtedly happens.

Below are the faces and roles that we assigned in 2018! We had three new additions to the group halfway through the year (Nikki Rubinstein, Lucy Liu and Adele Barughase) who haven’t been assigned a specific role yet.

```{r fig.cap = "Fig1. Organisers between 2017 and 2018"}
img <- readPNG("AllPhotos/organisers.png")
grid.raster(img)
```


# Be ready to pass the ball

The figure above might seem like a very large committee. However, due to different life and work committements, Saskia, Göknur and Roxane stepped down from the 2019 committee. On behalf of all the R-Ladies Melbourne I could not thank them more for all the help in building and growing this community! 
This raises an important discussion that as a group we need to have in the coming year: uphow to include new pgetnd get them up to speed with the organisation built so far. It is also a prerogative of a registered association to elect committee members every year, which means that after a while the current members should be substituted.  
We are really working hard towards making the R-Ladies Melbourne management accessible to new organising members. For us, this has meant so far, writing down rules and task that new peosple can refer to. This is because we should be able to pass the baton to new volunteers who can bring fresh ideas to the team. We are all at different stages of our careers, and we might all have different plans for the future but we all want the R-Ladies Melbourne to keep thriving. 

# Become a not-for-profit in Australia

As I mentioned before, different laws apply to different countries. Even within Australia, laws vary between the states. Since none of us has any law background, I firstly asked for support on Twitter and Facebook. That's when people started offering suggestion and I got initially directed towards the material provided by the [nfplaw](https://www.nfplaw.org.au/) website, which is not only for Victoria. There, you can find plenty of information about what it means to incorporate and it guides you through understanding whether you should consider incorporating. Everything is explained in a very easily accessible language so you don’t need to be a lawyer to get through it!
[Melissa Davis](https://www.wehi.edu.au/people/melissa-davis), a lab head in the Bioinformatics division at the Walter and Eliza Hall Institute, also offered invaluable help in guiding us through the rules in Victoria and suggested that we looked into [Consumer Affair Victoria (CAV)](https://www.consumer.vic.gov.au/clubs-and-fundraising/incorporated-associations/become-an-incorporated-association)'s rules for incorporating. Eventually, Lucy Liu volunteered to read through the CAV's rules and in our last committee meeting in December we established that we will finally incorporate the coming February!  


# My personal remarks about being R-Ladies organiser


These two years as co-organiser of the R-Ladies Melbourne gave me an excellent opportunity to grow both careerwise and from a personal point of view. Organising events with passionate and supportive colleagues and receiving positive feedback from the public was a super rewarding experience. In the last year as main organiser I had the opportunity to gain valuable leadership experience. This included mediating conflicts within the group; chairing the monthly meeting; thinking about future goals and looking for sponsors; think about new events that the members could benefit from. I had the chance to meet amazing people I learnt so much more about R which made me even more passionate about it and it made me really feel like an integral part of the great community. I expanded greatly the network of people that I know and can ask for support both in Melbourne and from other parts of the world and from both academia and industry, thanks to the amazing R-Ladies Slack community.

This is why I strongly encourage anyone to try and take on these organising roles. I am sure you won't be disappointed!

# Get involved 

If there is something else that you would like to know but I haven't discussed here please feel free to send us an email at: melbourne@rladies.org. 
Also, we are always looking for new speakers for seminars, workshops and new ideas! 

**If you would like to get involved as organiser or in other ways, we would love to hear from you**
  
You can use any of the means below to contact us:
  
* `r icon::fa("twitter",colour = "#88398A")` https://twitter.com/RLadiesMelb
* `r icon::fa("github",colour = "#88398A")` https://github.com/R-LadiesMelbourne
* `r icon::fa("meetup",colour = "#88398A")` https://www.meetup.com/R-Ladies-Melbourne/
* `r icon::fa("facebook",colour = "#88398A")` https://www.facebook.com/RladiesMelbourne/
* Email: melbourne@rladies.org

# Aknowledgements

* To produce this document I used some of the tips in [Pimp my Rmd](https://holtzy.github.io/Pimp-my-rmd/#use_dt_for_tables) by [Yan Holtz](https://github.com/holtzy)
* Thanks to my friend Steven Megaloudis who helped with proof reading parts of this post! Thanks also.especially to Sepideh for her helfpful suggestion as well to Marie and Saskia.

